Reply to: 2022-18044 Intentional release of native species undermines ecological stability

### 2022-12-25 rmd/reply_r2.Rmd
Update reply_r2.Rmd

> Thank you for your careful reading. However, this data point is not identified as an outlier; thus, there is no statistical justification for removing it from the analysis. Although the figure was shown on an ordinary scale, the analysis was carried out on a log-scale (see Methods). When we applied the Grubb's test to the log-transformed CV, the p-value was 0.176, indicating that our results were not strongly influenced by the highest value of CV (see R codes below). Also, we have confirmed that our results were robust even if we used robust regression with the MM method, which accounts for potential outliers in both response (log CV) and predictor variables (effective release). We hope this ameliorates the reviewer's concern.

@@

> Thank you for this comment. We agree with this opinion. However, we believe our analysis has already accounted for this aspect. The main response variable in our analysis (CV) is the aggregate measure of all species present in the community, namely: $CV = \frac{\sqrt{\sum \sigma^2_i + \sum \sum Cov_{ij}}}{\sum \mu_i}$ ($\sigma_i$ is the SD for species $i$). Therefore, the point raised by the reviewer is already accounted for in our model, albeit implicitly. Also, we wanted to remind the reviewer that our results indicated that the community SD was not influenced by intentional release. Although we cannot exclude the possible importance of relative community composition, our data suggest that it has a minimal influence on the dynamics (at least in our system).

>>>>

> Thank you for your careful reading. Give this comment, we checked whether this point strongly affects the overall pattern. When we applied the Grubb's test to the log-transformed CV, the p-value was 0.176, indicating that our results were not strongly influenced by the highest value of CV (see R codes below). Please note that, although the figure was shown on an ordinary scale, the analysis was carried out on a log-scale (see Methods).
>
> Also, we have confirmed that our results were robust even if we used robust regression with the MM method, which accounts for potential outliers in both response (log CV) and predictor variables (effective release).
>
> We hope this ameliorates the reviewer's concern.

@@

> Thank you for this comment. We agree with this opinion; therefore, our analysis was designed to account for this aspect. The main response variable in our analysis (CV) is the aggregate measure of all species present in the community, namely: $CV = \frac{\sqrt{\sum \sigma^2_i + \sum \sum Cov_{ij}}}{\sum \mu_i}$ ($\sigma_i$ is the SD for species $i$). As such, the point raised by the reviewer is already accounted for in our model, albeit implicitly.
>
> Also, we wanted to remind the reviewer that the relative community composition & species richness are the pathways through which intentional release affects community stability (see Theoretical predictions). **Intentional release changes relative abundance of unenhanced species, as our theory suggests.** Therefore, although our regression model does not include the effects of relative community composition explicitly, it is the part of the effect of intentional release. Due to the tight correlation between intentional release and community composition/richness, including both factors into a single model will create an issue of multicollinearity.
>
> In summary, we have already accounted for the point raised by the reviewer. We appreciate the input though!
